---
title: "Survey models for Gss10"
author: "Ben Brew"
date: "January 6, 2018"
output: html_document
---

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE}
###{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}


# If get_new_data is set to True,
# make sure that you are working within the "insider" virtualenv

# Libraries
library(tidyverse)
library(glmnet)
library(knitr)
library(Hmisc)
library(RColorBrewer)
library(plotly)
library(databrew)
library(ggmap)
library(reshape2)
library(memisc)
library(texreg)


# Turn off scientific notation
options(scipen = '999')

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, # Render report, even with errors
               cache = F)

# source functions
source('functions.R')

# Get all locations
if('preprocess_survey_data.RData' %in% dir('data')){
  load('data/preprocess_survey_data.RData')
} else { 
  source('global.R')
}
 
```

# General Social Survey 2010


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# get lfs data from survey list 
gss <- survey[[2]]

# make all characters
gss <- restructure_data_types(gss, convert_from  = 'character')

colnames(gss)[grepl('vismin', colnames(gss))]


```

## Self reported physical health

### health as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

summary(as.factor(gss$hw_gss10_mental_health))
# first recod health to two levels 
gss$hw_gss10_health_binary <- as.factor(ifelse(grepl('good|very|excellent', gss$hw_gss10_health), 
                                       'good health', 
                                       ifelse(grepl('poor|fair', gss$hw_gss10_health), 
                                              'poor_fair', 
                                              ifelse(grepl("Don't", gss$hw_gss10_health), 
                                                     NA, gss$hw_gss10_health))))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



## health as a function of gender, age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group' ,'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### health as a function of gender, age, highest edu

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group' , 'ed_gss10_highest_level_edu','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```
### health as a function of gender, age, highest edu, type of parents

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group' , 'ed_gss10_highest_level_edu', 'demo_gss10_type_parents','demo_gss10_sample_weight'),
                 outcome_var = 'hw_gss10_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


## Self reported mental health

### mental health as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# first recod health to two levels 
gss$hw_gss10_mental_health_binary <- as.factor(ifelse(grepl('very|excellent', gss$hw_gss10_mental_health), 
                                       'very_good_excellent', 
                                       ifelse(grepl('poor|fair', gss$hw_gss10_mental_health), 
                                              'poor_fair_good', 
                                              ifelse(gss$hw_gss10_mental_health == 'good', 'poor_fair_good',
                                                     ifelse(grepl("Don't", gss$hw_gss10_mental_health), 
                                                            NA, gss$hw_gss10_mental_health)))))



custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group','demo_gss10_personal_income', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')                                            
                
```


### mental health as a function of gender, age, income

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group','demo_gss10_personal_income', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

### mental health as a function of gender, age, income,edu

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group', 'demo_gss10_personal_income','demo_gss10_highest_level_edu','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### mental health as a function of gender, age, edu, marital status, income

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group', 'demo_gss10_highest_level_edu','demo_gss10_marital_status','demo_gss10_personal_income','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

### mental health as a function of gender, age, edu, marital status,inncome, active sports, active leisure

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group', 'demo_gss10_highest_level_edu','demo_gss10_marital_status','demo_gss10_personal_income' ,'hw_gss10_mins_active_sports', 'hw_gss10_mins_active_leisure','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

### mental health as a function of gender, age, edu, marital status,inncome, active sports, active leisure

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex','demo_gss10_age_group', 'demo_gss10_highest_level_edu','demo_gss10_marital_status','demo_gss10_personal_income' ,'hw_gss10_mins_active_sports', 'hw_gss10_mins_active_leisure', 'hw_gss10_workaholic','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_mental_health_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


## Self reported opinion oflife

### life as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# first recode life variable - right now 1 is disatisfied and 10 very satisfied - remove everything else 
gss$hw_gss10_life_binary <- ifelse(grepl('11|98|99', gss$hw_gss10_life), NA, gss$hw_gss10_life)
gss$hw_gss10_life_binary <- as.factor(ifelse(gss$hw_gss10_life_binary >= 8, '8-10', '1-5'))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

### life as a function of gender, age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### life as a function of gender, age, education

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### life as a function of gender, age, education, income, 

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### life as a function of gender, age, education, income, marital status

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### life as a function of gender, age, education, income, marital status, active sports, active leisure

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status


custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status', 'hw_gss10_mins_active_sports', 'hw_gss10_mins_active_leisure', 'demo_gss10_sample_weight'), 
                 outcome_var = 'hw_gss10_life_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



## Volunteering in last year

### volunteering as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


### volunteering as a function of gender, age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education, income

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education, income, marital status

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education, income, marital status, health, mental health

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status', 'hw_gss10_health','hw_gss10_mental_health', 'demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education, income, marital status, health, mental health, parents

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status', 'hw_gss10_health','hw_gss10_mental_health', 'demo_gss10_type_of_parents','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



### volunteering as a function of gender, age, education, income, marital status, health, mental health, parents,sleep, tv

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  ww_gss10_health, hw_gss10_mental_health, hw_gss10_life, gss$ce_gss10_vol_anywhere_last_year
# predictors: hw_gss10_age, hw_gss10_sex, ed_gss10_highest_level_edu, demo_gss10_type_of_parents, demo_gss10_marital_status, hw_gss_10_mins_night_sleep, hw_gss10_mins_tv, sf_gss10_mins_at_someone_else_home,
# hw_gss10_mins_active_sports, hw_gss10_mins_active_leisure, hw_gss10_workaholic, hw_gss10_main_source_stress, em_gss10_labour_force_status

# remove don't know from volunteer 
gss$ce_gss10_vol_binary <- as.factor(ifelse(grepl("Don't know", gss$ce_gss10_vol_anywhere_last_year), NA, 
                                  gss$ce_gss10_vol_anywhere_last_year))

custom_logit_mod(gss, 
                 model_vars = c('demo_gss10_sex', 'demo_gss10_age_group','demo_gss10_highest_level_edu','demo_gss10_personal_income','demo_gss10_marital_status', 'hw_gss10_health','hw_gss10_mental_health', 'demo_gss10_type_of_parents','hw_gss_10_mins_night_sleep', 'hw_gss10_mins_tv','demo_gss10_sample_weight'), 
                 outcome_var = 'ce_gss10_vol_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

## plots and visualizations