---
title: "Preliminary regressions for Labour Force survey"
author: "Ben Brew"
date: "January 5, 2018"
output: html_document
---
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE}
###{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}


# If get_new_data is set to True,
# make sure that you are working within the "insider" virtualenv

# Libraries
library(tidyverse)
library(glmnet)
library(knitr)
library(Hmisc)
library(RColorBrewer)
library(plotly)
library(databrew)
library(ggmap)
library(reshape2)
library(memisc)
library(texreg)


# Turn off scientific notation
options(scipen = '999')

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, # Render report, even with errors
               cache = F)

# source functions
source('../functions.R')

# Get all locations
if('preprocess_survey_data.RData' %in% dir('data')){
  load('../data/preprocess_survey_data.RData')
} else { 
  source('../global.R')
}
 
```

# Labour Force Survey 

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# get lfs data from survey list 
lfs <- survey[[1]]

# make all characters
lfs <- restructure_data_types(lfs, convert_from = 'character')


```

## Unemployment

### Unemployment as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_unemployed_only', 
                 weights = FALSE, 
                 mod_type = 'binomial')


```


### Unemployment as a function of gender and age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age', 'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_unemployed_only', 
                 weights = FALSE, 
                 mod_type = 'binomial')


```



### Unemployment as a function of gender, age, and student status


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age', 'ed_lfs_non_student','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_unemployed_only', 
                 weights = FALSE, 
                 mod_type = 'binomial')


```


### Unemployment as a function of gender, age, student status, and education

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age', 'ed_lfs_non_student','ed_lfs_highest_edu','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_unemployed_only', 
                 weights = FALSE, 
                 mod_type = 'binomial')


```


## Hourly wage as a function of gender
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_hourly_wages', 
                 weights = FALSE, 
                 mod_type = 'gaussian')


```

## Hourly wage as a function of gender and age
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_hourly_wages', 
                 weights = FALSE, 
                 mod_type = 'gaussian')


```

## Hourly wage as a function of gender, age, and education
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age','ed_lfs_highest_edu','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_hourly_wages', 
                 weights = FALSE, 
                 mod_type = 'gaussian')


```

# Hourly wage as a function of gender, age, education, and class of worker 
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age','ed_lfs_highest_edu','em_lfs_class_of_worker','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_hourly_wages', 
                 weights = FALSE, 
                 mod_type = 'gaussian')


```

# Hourly wage as a function of gender, age, education, class of worker, and union
em_lfs_class_of_worker  
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex', 'demo_lfs_age','ed_lfs_highest_edu','em_lfs_class_of_worker', 'em_lfs_union_membership' ,'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_hourly_wages', 
                 weights = FALSE, 
                 mod_type = 'gaussian')



```

# NEET as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_neet', 
                 weights = FALSE, 
                 mod_type = 'binomial')



```

# NEET as a function of gender and age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_neet', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


# NEET as a function of gender, age, and highest education

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'ed_lfs_highest_edu','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_neet', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```



# hours worked as a function of gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_actual_hours_per_week_all_jobs', 
                 weights = FALSE, 
                 mod_type = 'gaussian')



```



# hours worked as a function of gender, age

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_actual_hours_per_week_all_jobs', 
                 weights = FALSE, 
                 mod_type = 'gaussian')


```



# hours worked as a function of gender, age, education
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'ed_lfs_highest_edu','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_actual_hours_per_week_all_jobs', 
                 weights = FALSE, 
                 mod_type = 'gaussian')

```




# hours worked as a function of gender, age, education, and union memebership
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'ed_lfs_highest_edu','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_actual_hours_per_week_all_jobs', 
                 weights = FALSE, 
                 mod_type = 'gaussian')

```


# hours worked as a function of gender, age, education, union memebership, and class of worker
```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}
# outcomes :  em_lfs_hourly_wages, em_lfs_neet, em_lfs_actual_hours_per_week_main_job, em_lfs_unemployed_only
custom_logit_mod(lfs, 
                 model_vars = c('demo_lfs_sex' ,'demo_lfs_age', 'ed_lfs_highest_edu','em_lfs_class_of_worker ','demo_lfs_sample_weight'), 
                 outcome_var = 'em_lfs_actual_hours_per_week_all_jobs', 
                 weights = FALSE, 
                 mod_type = 'gaussian')

```


