---
title: "Survey stats for osduhs"
author: "Ben Brew"
date: "January 6, 2018"
output: html_document
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE}
###{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}


# If get_new_data is set to True,
# make sure that you are working within the "insider" virtualenv

# Libraries
library(tidyverse)
library(glmnet)
library(knitr)
library(Hmisc)
library(RColorBrewer)
library(plotly)
library(databrew)
library(ggmap)
library(reshape2)
library(memisc)
library(texreg)


# Turn off scientific notation
options(scipen = '999')

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, # Render report, even with errors
               cache = F)
# source functions
source('../functions.R')

# Get all locations
if('preprocess_survey_data.RData' %in% dir('data')){
  load('../data/preprocess_survey_data.RData')
} else { 
  source('../global.R')
}
 
 
```

# Osduhs


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# get lfs data from survey list 
osduhs <- survey[[10]]

# make all characters
osduhs <- restructure_data_types(osduhs, convert_from  = 'character')
colnames(osduhs)[grepl('weight', colnames(osduhs))]

```


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# make safe at school binary
osduhs$safe_at_school_binary <- as.factor(ifelse(grepl(' agree', osduhs$ds_osduhs_safe_at_school),
                                       'agree', 
                                       ifelse(grepl('disagree', osduhs$ds_osduhs_safe_at_school),
                                              'disagree', osduhs$ds_osduhs_safe_at_school)))

# make got bullied binary
osduhs$got_bullied_binary <- as.factor(ifelse(grepl('was not', osduhs$ds_osduhs_sept_got_bullied_school),
                                    'not bullied', 
                                    ifelse(grepl('about|daily|month', osduhs$ds_osduhs_sept_got_bullied_school),
                                           'got bullied', osduhs$ds_osduhs_sept_got_bullied_school)))

# make feel good about self binary
osduhs$feel_good_about_self <- as.factor(ifelse(grepl(' agree', osduhs$hw_osduhs_feel_good_about_self),
                                       'agree', 
                                       ifelse(grepl('disagree', osduhs$hw_osduhs_feel_good_about_self),
                                              'disagree', osduhs$hw_osduhs_feel_good_about_self)))


```


## Safe at school 

### safe at as a function of race

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcome: ds_osduhs_safe_at_school, hw_osduhs_12_months_consider_suicide,  ds_osduhs_sept_did_bullied_school, hw_osduhs_feel_good_about_self

# predcitros: gender, age, race, demo_osduhs_mother_home, demo_osduhs_step_mother_home, demo_osduhs_adop_mother_home
# demo_osduhs_father_home, demo_osduhs_step_fatherr_home, demo_osduhs_adop_father_home, demo_osduhs_how_long_live_in_canada # demo_osduhs_hrs_per_day_social_media, ed_osduhs_avg_marks, ed_osduhs_travel_to_school, demo_osduhs_father_edu, 
# demo_osduhs_mother_edu, hw_osduhs_head_injury_lifetime_freq

custom_logit_mod(osduhs, 
                 model_vars = c('race', 'demo_osduhs_pop_weight'),
                 outcome_var = 'safe_at_school_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```

## Safe at school 

### safe at as a function of race, gender

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcome: ds_osduhs_safe_at_school, hw_osduhs_12_months_consider_suicide,  ds_osduhs_sept_did_bullied_school, hw_osduhs_feel_good_about_self

# predcitros: gender, age, race, demo_osduhs_mother_home, demo_osduhs_step_mother_home, demo_osduhs_adop_mother_home
# demo_osduhs_father_home, demo_osduhs_step_fatherr_home, demo_osduhs_adop_father_home, demo_osduhs_how_long_live_in_canada # demo_osduhs_hrs_per_day_social_media, ed_osduhs_avg_marks, ed_osduhs_travel_to_school, demo_osduhs_father_edu, 
# demo_osduhs_mother_edu, hw_osduhs_head_injury_lifetime_freq

custom_logit_mod(osduhs, 
                 model_vars = c('race', 'gender', 'demo_osduhs_pop_weight'),
                 outcome_var = 'safe_at_school_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


## Safe at school 

### safe at as a function of race, gender, mom, dad, 

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcome: ds_osduhs_safe_at_school, hw_osduhs_12_months_consider_suicide,  ds_osduhs_sept_did_bullied_school, hw_osduhs_feel_good_about_self

# predcitros: gender, age, race, demo_osduhs_mother_home, demo_osduhs_step_mother_home, demo_osduhs_adop_mother_home
# demo_osduhs_father_home, demo_osduhs_step_fatherr_home, demo_osduhs_adop_father_home, demo_osduhs_how_long_live_in_canada # demo_osduhs_hrs_per_day_social_media, ed_osduhs_avg_marks, ed_osduhs_travel_to_school, demo_osduhs_father_edu, 
# demo_osduhs_mother_edu, hw_osduhs_head_injury_lifetime_freq

custom_logit_mod(osduhs, 
                 model_vars = c('race', 'gender', 'demo_osduhs_mother_home', 'demo_osduhs_step_mother_home', 'demo_osduhs_adop_mother_home', 'demo_osduhs_father_home', 'demo_osduhs_step_father_home', 'demo_osduhs_adop_father_home', 'demo_osduhs_pop_weight'),
                 outcome_var = 'safe_at_school_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


## Safe at school 

### safe at as a function of race, gender, mom, dad, live in canada, hrs on social media, 

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcome: ds_osduhs_safe_at_school, hw_osduhs_12_months_consider_suicide,  ds_osduhs_sept_did_bullied_school, hw_osduhs_feel_good_about_self

# predcitros: gender, age, race, demo_osduhs_mother_home, demo_osduhs_step_mother_home, demo_osduhs_adop_mother_home
# demo_osduhs_father_home, demo_osduhs_step_fatherr_home, demo_osduhs_adop_father_home, demo_osduhs_how_long_live_in_canada # demo_osduhs_hrs_per_day_social_media, ed_osduhs_avg_marks, ed_osduhs_travel_to_school, demo_osduhs_father_edu, 
# demo_osduhs_mother_edu, hw_osduhs_head_injury_lifetime_freq

custom_logit_mod(osduhs, 
                 model_vars = c('race', 'gender', 'demo_osduhs_mother_home', 'demo_osduhs_step_mother_home', 'demo_osduhs_adop_mother_home', 'demo_osduhs_father_home', 'demo_osduhs_step_father_home', 'demo_osduhs_adop_father_home', 'demo_osduhs_how_long_live_in_canada', 'demo_osduhs_hrs_per_day_social_media', 'demo_osduhs_pop_weight'),
                 outcome_var = 'safe_at_school_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```


## Safe at school 

### safe at as a function of race, gender, mom, dad, live in canada, hrs on social media, avg marks, travel to school, parents education, head injury

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, results = 'asis',error= FALSE}

# outcome: ds_osduhs_safe_at_school, hw_osduhs_12_months_consider_suicide,  ds_osduhs_sept_did_bullied_school, hw_osduhs_feel_good_about_self

# predcitros: gender, age, race, demo_osduhs_mother_home, demo_osduhs_step_mother_home, demo_osduhs_adop_mother_home
# demo_osduhs_father_home, demo_osduhs_step_fatherr_home, demo_osduhs_adop_father_home, demo_osduhs_how_long_live_in_canada # demo_osduhs_hrs_per_day_social_media, ed_osduhs_avg_marks, ed_osduhs_travel_to_school, demo_osduhs_father_edu, 
# demo_osduhs_mother_edu, hw_osduhs_head_injury_lifetime_freq

custom_logit_mod(osduhs, 
                 model_vars = c('race', 'gender', 'demo_osduhs_mother_home', 'demo_osduhs_step_mother_home', 'demo_osduhs_adop_mother_home', 'demo_osduhs_father_home', 'demo_osduhs_step_father_home', 'demo_osduhs_adop_father_home', 'demo_osduhs_how_long_live_in_canada', 'demo_osduhs_hrs_per_day_social_media', 'ed_osduhs_avg_marks', 'ed_osduhs_travel_to_school', 'demo_osduhs_father_edu', 'demo_osduhs_mother_edu', 'hw_osduhs_head_injury_lifetime_freq' , 'demo_osduhs_pop_weight'),
                 outcome_var = 'safe_at_school_binary', 
                 weights = FALSE, 
                 mod_type = 'binomial')

```
