---
title: YouthREX tables
author: www.databrew.cc
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: yeti
---


<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
      font-family: lato, sans-serif;
  }
td {  /* Table  */
  font-size: 10px;
}
h1.title {
  font-weight: bold;
  font-size: 40px;
  font-family: lato, sans-serif;
}
h1 { /* Header 1 */
  font-size: 36px;
  text-decoration: underline;
  font-weight: bold;
  font-family: lato, sans-serif;
}
h2 { /* Header 2 */
  font-size: 32px;
  font-weight: bold;
  font-family: lato, sans-serif;
}
h3 { /* Header 3 */
  font-size: 24px;
  font-weight: bold;
  font-family: lato, sans-serif;
}

h4 { /* Header 4 */
  font-size: 20px;
  font-weight: bold;
  font-family: lato, sans-serif;
}

h5 { /* Header 5 */
  font-size: 18px;
  font-family: lato, sans-serif;
}

h6 { /* Header 6 */
  font-size: 15px;
  font-family: lato, sans-serif;
}

code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages (load child-specific packages in their respective files)
library(raster)
library(stringr)
library(xtable)
library(knitr)
library(Hmisc)
library(ggmap)
library(dplyr)
library(maptools)
library(gpclib)
library(ggplot2)
library(DT)
library(printr)
library(RColorBrewer)
# install the above via:
# install.packages(
#   'printr',
#   type = 'source',
#   repos = c('http://yihui.name/xran', 'http://cran.rstudio.com')
# )
library(raster)
library(stringr)
library(tidyr)
library(highcharter)
library(rstan)
library(rstanarm)
library(tidyr)
library(ggplot2)
library(highcharter)
library(htmlwidgets)
library(sparkline)
library(zoo)
library(lubridate)
# devtools::install_github('htmlwidgets/sparkline')

# Basic knitr options
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r}
creation_date <- as.Date(Sys.Date())
source('../global.R', chdir = T)
source('../functions.R')
```

# Executive summary



```{r, results = 'asis'}
library(DT)
# table_list <- lapply(split(iris, iris[, 5]), prettify)
# titles <- names(table_list)

# Generate a list of tables
already_done <- c()
table_list <- list()
titles <- c()
scs <- sort(unique(census_dict$sub_category))
scs <- scs[!scs %in% c('demographic', 'year')]
ages <- sexes <- pobs <- vms <- ais <- geo_codes <- percents <- c(TRUE, FALSE)
years <- c(2001, 2006, 2011)
counter <- 0
for(sc in scs){
  counter <- counter + 1
  titles[counter] <- paste0('\n# ', Hmisc::capitalize(gsub('_', ' ', sc)))
  table_list[[counter]] <- NA
  for(age in ages){
    for(sex in sexes){
      for(pob in pobs){
        for(vm in vms){
          for(ai in ais){
            for(geo_code in geo_codes){
              for(percent in percents){
                trues <- c(ifelse(age, 'age', NA),
                           ifelse(sex, 'sex', NA),
                           ifelse(pob, 'pob', NA),
                           ifelse(vm, 'vm', NA),
                           ifelse(ai, 'ai', NA),
                           ifelse(geo_code, 'geo_code', NA),
                           ifelse(percent, 'percent', NA),
                           ifelse(!is.null(sc), sc, NA))
                trues <- trues[!is.na(trues)]
                trues <- sort(unique(trues))
                lt <- length(trues)
                trues <- paste0(trues, collapse = ',')

                if(lt <= 4 & !trues %in% already_done){
                counter <- counter + 1
                message(trues)

                already_done <- c(already_done, trues)
                
                nothing <- !age & !sex & !pob & !vm & !ai & !geo_code
                title <- paste0('Raw ', gsub('_', ' ', sc),
                                ' data',
                                ifelse(nothing, '', ' by '),
                                ifelse(age, 'age, ', ''),
                                ifelse(sex, 'sex, ', ''),
                                ifelse(pob, 'place of birth, ', ''),
                                ifelse(vm, 'visible minority status, ', ''),
                                ifelse(ai, 'aboriginal identity, ', ''),
                                ifelse(geo_code, 'geography, ', ''))
                if(substr(title, nchar(title) - 1, nchar(title)) == ', '){
                  title <- substr(title, 1, nchar(title) - 2)
                }
                title <- paste0(title,
                                ifelse(percent, ' (%)', ''))
                titles[counter] <- paste0('\n## ', title)
                table_list[[counter]] <-
                  prettify_scroll(censify(age = age,
                          sex = sex,
                          pob = pob,
                          vm = vm,
                          ai = ai,
                          geo_code = geo_code,
                          years = c(2001, 2006, 2011),
                          sc = sc,
                          percent = percent),
                          download_options = TRUE,
                          no_scroll = FALSE,
                          nrows = 20,
                          scroll_x = TRUE)
                }

                
                
                # message(counter)
              }
            }
          }
        }
      }
    }
  }
}
```

This report contains `r counter - length(scs)` tables from the YouthREX Ontario census data. 
```{r}
headers <- unlist(lapply(table_list, function(x){length(x)})) == 1
chunks <- paste0(titles,
                 "\n\n", 
                 paste0(ifelse(headers, '', '```{r}\ntable_list[['),
                        ifelse(headers, '', 1:length(table_list)),
                        ifelse(headers, '', ']]\n```')), 
                 "\n\n")

# Write our order / child-calls to a doc
file_connection <- file('children.Rmd')
writeLines(paste0('---\noutput: html_document\n---\n\n', 
                  chunks), 
           file_connection)
close(file_connection)
```


```{r child='children.Rmd', echo = FALSE}
# Now, we simply include "children.Rmd" to construct our doc
# (ie, children is the child doc, and each section is a grandchild)
```

```{r, results='hide'}
# Having already called the auto-generated children.Rmd, we can delete it
file.remove('children.Rmd')
```

